Selective electroporation of the viral envelope

### 2021-04-15 documents/lessons_learned.tex
Convert to differential equation
DoF error

>>>>

the os community has figured out that investment in open work comes back;

is there a way to "sign" gel images (maybe from the gel-doc itself?) so that manipulation is obvious?

an interesting thing is searchability. I often don't come back to notes because it's easier and more likely I'll get a relevant result by googling again! future lab notebook should have a live and very effective search.

Why do problems keep happening? Why do bugs which other people have hit keep recurring? Why does bad science even happen?
